---
title: "ipedals, a data package about higher education"
author: "Justin Myers"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ipedals}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(dplyr)
library(magrittr)
```

ipedals is designed to simplify access to [IPEDS][], the Integrated
Postsecondary Education Data System from the U.S. Department of Education's
[National Center for Education Statistics][NCES].

[IPEDS]: https://nces.ed.gov/ipeds/
[NCES]: https://nces.ed.gov/

IPEDS consists of a collection of surveys completed by most colleges and
universities in the United States.

## Table names

The ipedals package centers around individual tables of survey data, since
that's how IPEDS itself is organized.

These are named with the combination of an academic year and one or more
abbreviations; for example, `ADM2016` contains information about admissions for
fall 2016.

This package eventually will include a way to look up these IDs from within R,
but for now, visit <https://nces.ed.gov/ipeds/datacenter/DataFiles.aspx>.

## Usage

Pass a table ID to `ipedals::ipeds_table`, and get back a list with several
useful properties:

```{r, warning = FALSE, message = FALSE, results = "hide"}
hd2016 <- ipedals::ipeds_table("HD2016")
```
```{r}
hd2016$table
```
```{r}
hd2016$variables %>% select(varname, varTitle)
```
```{r}
hd2016$codebook
```

## TODO

*   Explain IPEDS in more detail so people know what they're getting
*   Add table ID lookup
